Efficiently stable presentations from error-correcting codes

### 2023-10-24 efficient_stability.tex
notes in appendix

\begin{proof}[Proof sketch]
\mnote{This proof sketch is very confusing. We think of the elements of $P_k$ as $\pm \sigma_X(a)\sigma_Z(b)$, not as $J^{\pm 1}(a,b)$. This is a parametrization of the generators in the specific presentation we provided, and which does not play a role here in the proof. Actually, this is part of what is confusing. The corollary is essentially that almost homomorphisms w.r.t the above presentation of $P_k$ can be translated to almost homs of $P_k$ w.r.t the multiplication table pres without changing the $\eps$ too much. We developed the proper language to make Corollary \ref{cor:Pauli-brading_is_stable} much shorter. We should have just stated that the presentation we gave for $P_k$ is stable, and furthermore, that when $J$ is mapped to $-1$, then the close by representation must be of the form $\Id\otimes P_k$. Anyway, maybe we can discuss this a bit and then I'll do the changes. Didn't want to mess up if this is the way you wanted everything to look like.  }\tnote{You're right. This is partly because I changed the presentation a couple times in the past, and propagated incorrectly. What you suggest for the proof seems to be what I wrote for the sketch though, up to the mismatches in terms of notation, etc. If you can change to your idea that's good for me, thanks}

The idea is the following: The maps $\phi_X,\phi_Z$ induce an $\eps$-approximate representation of the Pauli group with respect to the presentation \eqref{eq:almost_mult_table_pres_of_Pauli}. From that, we can use the canonical form of elements in $\pauli_k$ to create an $O(\eps)$-approximate representation of the multiplication table presentation of $\pauli_k$ --- define $\phi:\pauli_k \to \mU(\mM)$ by $\phi((-1)^c \sigma_X(a)\sigma_Z(b))= (-1)^c \phi_X(a)\phi_Z(b)$, where $c\in \{\pm 1\}$ and $a,b\in \Z_2^k$. Applying Gowers--Hatami (Theorem \ref{thm:gh}), we deduce the corollary.
\end{proof}

@@

    We denote by $\mM_\Phi=\bigoplus_{\alpha\in \Phi}\mM\subseteq \mM_\infty$ and by $\mM_\alpha$ the copy of $\mM$ at the $\alpha\in \Phi$ position.
    Let $w_i=\mu_R(R_i)$, namely the probability that $\mu_R$ samples a relation from the orbit $R_i$. Then, for every $r\in R_i$, we have 

@@

    \forall r\in R\ \colon\ \ |\rho'(r)-\Id\|_\tau^2\leq \max({\nicefrac{1}{w_i}})\cdot\eps,

@@

which in turn means that $\rho'$ is a $\max({\nicefrac{1}{w_i}})\cdot\eps$-approximate representation in the $L^\infty$ sense. 

@@

    By applying this construction on the example from the beginning of the appendix, the resulting $\rho'$ is a $\nicefrac{2|E|}{\binom{k}{2}}$-approximate representation in the $L^\infty$ setup of \eqref{eq:z2-efficient}.

@@

Let $\varphi'\colon \Gamma\to \mU(\mN)$ be a genuine representation of $\Gamma$ satisfying 

@@

\end{split},

@@

Since the $L^\infty$ distance between functions is larger than the $L^1$ distance between them (with respect to any fully supported measure $\mu_S$), we conclude that a lower bound of $f(\eps)$ on the modulus of stability of a sufficiently symmetric presentation induces a lower bound of $\frac{\min{w_i}}{3}f(\eps)$.

>>>>

\begin{proof}[Proof sketch]
%\mnote{This proof sketch is very confusing. We think of the elements of $P_k$ as $\pm \sigma_X(a)\sigma_Z(b)$, not as $J^{\pm 1}(a,b)$. This is a parametrization of the generators in the specific presentation we provided, and which does not play a role here in the proof. Actually, this is part of what is confusing. The corollary is essentially that almost homomorphisms w.r.t the above presentation of $P_k$ can be translated to almost homs of $P_k$ w.r.t the multiplication table pres without changing the $\eps$ too much. We developed the proper language to make Corollary \ref{cor:Pauli-brading_is_stable} much shorter. We should have just stated that the presentation we gave for $P_k$ is stable, and furthermore, that when $J$ is mapped to $-1$, then the close by representation must be of the form $\Id\otimes P_k$. Anyway, maybe we can discuss this a bit and then I'll do the changes. Didn't want to mess up if this is the way you wanted everything to look like.  }\tnote{You're right. This is partly because I changed the presentation a couple times in the past, and propagated incorrectly. What you suggest for the proof seems to be what I wrote for the sketch though, up to the mismatches in terms of notation, etc. If you can change to your idea that's good for me, thanks}
The idea is the following: The maps $\phi_X,\phi_Z$ induce an $\eps$-approximate representation of the Pauli group with respect to the presentation \eqref{eq:almost_mult_table_pres_of_Pauli}. From that, we can use the canonical form of elements in $\pauli_k$ to create an $O(\eps)$-approximate representation of the multiplication table presentation of $\pauli_k$ --- define $\phi:\pauli_k \to \mU(\mM)$ by $\phi((-1)^c \sigma_X(a)\sigma_Z(b))= (-1)^c \phi_X(a)\phi_Z(b)$, where $c\in \{\pm 1\}$ and $a,b\in \Z_2^k$. Applying Gowers--Hatami (Theorem \ref{thm:gh}), we deduce the corollary.
\end{proof}

@@

    We denote by $\mM_\Phi=\bigoplus_{\alpha\in \Phi}\mM\subseteq \mM_\infty$ and by $\mM_\alpha$ the copy of $\mM$ at the $\alpha\in \Phi$ position.\tnote{Is it canonical what is the trace on $\mM_\Phi$? In the calculation below you assume a uniform weighted average, is it useful to say it?}
    Let $w_i=\mu_R(R_i)$, namely the probability that $\mu_R$ samples a relation from the orbit $R_i$. Then, for every $r\in R_i$, we have \tnote{For the second line, is it clear that we get uniform over $R_i$?}

@@

    \forall r\in R\ \colon\ \|\rho'(r)-\Id\|_\tau^2\leq \max({\nicefrac{1}{w_i}})\cdot\eps,

@@

which in turn means that $\rho'$ is a $\max_i\{{\nicefrac{1}{w_i}}\}\cdot\eps$-approximate representation in the $L^\infty$ sense. 

@@

    By applying this construction on the example from Claim~\ref{claim:appendix1}, the resulting $\rho'$ is a $\nicefrac{2|E|}{\binom{k}{2}}$-approximate representation of \eqref{eq:z2-efficient} in the $L^\infty$ sense.\tnote{Can we expand on this? Any permutation is an automorphism, right? So we end up having two classes of relations, and $w_1=w_2=1/2$. It might just be worth spelling out}

@@

Let $\varphi'\colon \Gamma\to \mU(\mN)$ be a genuine representation of $\Gamma$ satisfying \tnote{Is the $1/|\Phi|$ in front correct? Or maybe I'm missing how the $\tau_\infty$ is normalized exactly. It just sums over the $\alpha$'s?}\tnote{Also, I'm not sure I understood your starting point. You want to assume that $\varphi'$ is $L_\infty$-close, right? Here you only do $L_1$. Is this what the last sentence of the proof is supposed to justify? If so, perhaps better epxlain here.}

@@

\end{split}\;,

@@

Since the $L^\infty$ distance between functions is larger than the $L^1$ distance between them (with respect to any fully supported measure $\mu_S$), we conclude that a lower bound of $f(\eps)$ on the modulus of stability of a sufficiently symmetric presentation induces a lower bound of $\frac{\min{w_i}}{3}f(\eps)$ \tnote{on? (I know, but maybe we should say?)}.
